\documentclass[12pt]{article}


%\usepackage{fullpage,epsfig,wrapfig,url,palatino,color}
\usepackage{epsfig,wrapfig,url,palatino,color}

\pagestyle{plain}

\renewcommand{\baselinestretch}{1.}

\setlength{\topmargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\footskip}{0.2in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{0in}

\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.99}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{0.01}
\renewcommand{\dbltopfraction}{0.99}
\renewcommand{\dblfloatpagefraction}{0.01}

\pagestyle{empty}

\begin{document}

{\bf PART 1: THIN SHELL TOOL} 
\hfill Participant ID \verb+_______+
\vspace{0.3in}

What did you think was useful or interesting about this tool?
\vspace{1.3in}

Please rate the following potential features from 1-5, where 1 is not useful at all and 5 is highly useful: \\

\verb+___+ save/open dialog\\
\verb+___+ option to change the height of points\\
\verb+___+ visualization of the difference between an imported mesh and the optimized mesh\\
\verb+___+ visualization of materials used in the structure\\
\verb+___+ visualization of thickness of the structure


\vspace{0.3in}

Please list any other features that would have been useful in designing thin-shell structures.
\vspace{1.5in}




Describe or sketch some structures that you were unable to create due to limitations of the software.
\vspace{1in}



\newpage
{\bf PART 2: DESIGN METHOD COMPARISON} 
\hfill Participant ID \verb+_______+
\vspace{0.3in}

Rate the usefulness of various design tools in the following scenarios from 1-5,
where 1 is not useful at all and 5 is highly useful:


\vspace{0.15in}


Schematic Design (early-stage architectural design)\\
\verb+___+ paper \& pencil sketching \\
\verb+___+ traditional computer software \\
\verb+___+ thin-shell design tool \\

Team design meetings with architects \& engineering consultants\\
\verb+___+ paper \& pencil sketching \\
\verb+___+ traditional computer software \\
\verb+___+ thin-shell design tool \\

Presentation of preliminary or final designs to the client\\
\verb+___+ paper \& pencil sketching \\
\verb+___+ traditional computer software \\
\verb+___+ thin-shell design tool \\


\vspace{0.1in}

Additional comments or scenarios where these methods are most useful
\vspace{0.15in}

\hspace*{0.3in} 
Paper \& pencil sketching:
\vspace{1in}

\hspace*{0.3in} 
Traditional computer software:
\vspace{1in}

\hspace*{0.3in} 
Thin-shell design tool:
\vspace{1in}

Are there any other design tools that would be more useful than those listed above
in any of the scenarios?


\newpage
{\bf PARTICIPANT BACKGROUND \& EXPERIENCE}
\hfill Participant ID \verb+_______+
\vspace{0.3in}

\renewcommand\arraystretch{2}

\begin{tabular}{l@{\hspace{0.3in}}l}
Completed degree(s): 
& \verb+______________________________________+ \\
Degree(s) in progress: 
& \verb+______________________________________+ \\
%
\begin{minipage}[b]{1.8in}
\begin{flushleft}
~\\~\\\# of years of \\ architectural \\ education:
\end{flushleft}
\end{minipage}
& \verb+______________________________________+ \\
%
\begin{minipage}[b]{1.8in}
\begin{flushleft}
~\\~\\\# of years of \\ visual arts education:
\end{flushleft}
\end{minipage}
& \verb+______________________________________+ \\
%
\begin{minipage}[b]{1.8in}
\begin{flushleft}
~\\~\\\# of years of \\ architectural experience \\ (internships/jobs): 
\end{flushleft}
\end{minipage}
& \verb+______________________________________+ \\
%
\begin{minipage}[b]{1.8in}
\begin{flushleft}
~\\~\\\# of years of \\ visual arts experience \\ (internships/jobs): 
\end{flushleft}
\end{minipage}
& \verb+______________________________________+ \\
%
\begin{minipage}[b]{1.8in}
\begin{flushleft}
~\\~\\other relevant education/experience \\ (please describe):
\end{flushleft}
\end{minipage}
& \verb+______________________________________+ \\
%
\end{tabular}

\renewcommand\arraystretch{1.0}

\vspace{0.5in}

{\bf CONSENT FOR PUBLICATION}
\vspace{0.1in}

After completing this survey:
\vspace{0.3in}

\verb+____+~~
\begin{minipage}[t]{5.8in}
I give permission for use of any or all of the thin-shell designs
and my comments in academic
publications. This information will be anonymous and my participation
in the study will not be revealed.
\end{minipage}
\vspace{0.3in}

\verb+____+~~
I give permission for use of selected information.  (please describe)
\vspace{0.3in}

\verb+____+~~
I do not give permission for use of any of this information at this time.


\newpage
{\bf PARTICIPANT CONTACT INFORMATION}
\hfill Participant ID \verb+_______+
\vspace{0.3in}


RPI requires us to collect the following basic contact information
from all participants in this user study.  Your participation will
remain confidential, and this portion of the record will be securely
stored by Professor Barbara Cutler.

\vspace{0.2in}

\renewcommand\arraystretch{2.0}

\begin{tabular}{r@{\hspace{0.3in}}l}
Name: 
& \verb+______________________________________+ \\
E-mail: 
& \verb+______________________________________+ \\
Home mailing address: 
& \verb+______________________________________+ \\
& \verb+______________________________________+ \\
& \verb+______________________________________+ \\
\end{tabular}

\renewcommand\arraystretch{1.0}

\vspace{0.5in}

Participants for this study will be compensated for their time in the
form of a gift certificate at the rate of \$10 per hour.  This
compensation is not contingent upon the subject completing the entire
study and will be prorated if the subject withdraws.  For IRS income
reporting purposes, RPI must also collect the social security number
and RIN number of participants who accept compensation. 
\vspace{0.1in}

\renewcommand\arraystretch{1.75}
\begin{tabular}{r@{\hspace{0.3in}}l}
\hspace{0.45in}Social Security number:
& \verb+______________________________________+ \\
\hspace{0.45in}RIN number:
& \verb+______________________________________+ \\
\verb+______+ & I decline the compensation
\end{tabular}

\renewcommand\arraystretch{1.0}

\newpage

\vspace*{0.5in}

Thanks for participating in our user study!\\

\vspace{0.2in}

Allan Pendergrast\\
Masters Student\\
Department of Computer Science\\
Rensselaer Polytechnic Institute\\
{\tt pender@rpi.edu}\\
\url{http://www.rpi.edu/~pender/}\\


Barb Cutler\\
Assistant Professor\\
Department of Computer Science\\
Rensselaer Polytechnic Institute\\
{\tt cutler@cs.rpi.edu}\\
\url{http://www.cs.rpi.edu/~cutler/}\\


\end{document}
